Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-31 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:31	20:48:57	(Mon31.Aug)

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{\emph{Determining LCA window type}: MVDR images with typical frequency responses chosen for various pixel regions.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@

To test the performance of the MVDR and LCA beamformers, we have processed data aquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2009}. It is a high resolution synthetic aperture sonar with array length 1.2\;m, 100\;kHz operating frequency, a bandwidth of 40\;kHz and 25$^\circ$ opening angle.

Two different scenes will be presented. One of the 1500 dwt oiltanker wreck Holmengraa lying at a slanted seabed at 77\;m depth outside of Horten, Norway~\cite{holmengraa}. It measures 68\;m by 9\;m and fills most of the highlit sector. The other scene is of an iron cross connected to a an anchor (fig ???).

@@

Assuming that a robust MVDR computes the optimal windows in the minimum variance sense, it makes sense to study them. For this we selected a scene of the oil tanker wreck Holmengraa, which lies at a slanted seabed at nearly 100\;m depth. A sectorscan image of a single ping of data collected by the HISAS1030 syntetic aperture sonar is shown in \Fig{mvdr_selected_windows}, along with the window responses MVDR typically chooses in shadow, speckle and highlight regions in this image. A fairly agressive yet stable set of parameters for MVDR where used; subarray size $L=16$, temporal averaging of $K=1$, and $d=1\%$ of diagonal loading.

While MVDR is free to choose non-symmetric windows, we can observe from \Fig{mvdr_selected_windows} that it prefers symmetric ones. In shadow and speckle the windows are fully symmetric, while in highlight the windows are approximately symmetric within the opening angle of the sonar. The peak sidelobe levels are between that of the rectangular and Hamming window.

This correspond to Kaiser windows with $\beta$-values of 0 and 2, respectively.
\Fig{oversampling_mosaic_bounds_beta} illustrates which $\beta$-value LCA prefers for different regions in the cross image.

Kaiser

>>>>

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{\emph{Determining LCA window type}: MVDR images with typical frequency responses chosen for various pixel regions.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight to allow the steering there.} }\label{mvdr_selected_windows}
\end{figure*}

@@

To test the performance of the MVDR and LCA beamformers, we have processed data acquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2009}. It is a high resolution synthetic aperture sonar with array length 1.2\;m, 100\;kHz operating frequency, a bandwidth of 40\;kHz and 25$^\circ$ opening angle.

Two different scenes will be presented. One of the 1500 DWT oiltanker wreck Holmengraa lying at a slanted seabed at 77\;m depth outside of Horten, Norway~\cite{holmengraa}. It measures 68\;m by 9\;m and fills most of the highlighted sector. The other scene is of an iron cross connected to a an anchor (fig ???).

@@

Assuming that a robust MVDR computes the optimal windows in the minimum variance sense, it makes sense to study them. For this we selected a scene of the oil tanker wreck Holmengraa, which lies at a slanted seabed at nearly 100\;m depth. A sectorscan image of a single ping of data collected by the HISAS1030 syntetic aperture sonar is shown in \Fig{mvdr_selected_windows}, along with the window responses MVDR typically chooses in shadow, speckle and highlight regions in this image. A fairly aggressive yet stable set of parameters for MVDR where used; subarray size $L=16$, temporal averaging of $K=1$, and $d=1\%$ of diagonal loading.

While MVDR is free to choose non-symmetric windows, we can observe from \Fig{mvdr_selected_windows} that it prefers symmetric ones. In shadow and speckle the windows are fully symmetric, while in highlight the windows are approximately symmetric within the opening angle of the sonar. The peak sidelobe levels are between that of the rectangular and Hamming window. This correspond to Kaiser windows with $\beta$-values of 0 and 2, respectively.

\Fig{oversampling_mosaic_bounds_beta} illustrates which $\beta$-value LCA prefers for different regions in the image of the cross.
